---
title: "Homework#2RG"
author: "Ryan Gandolfi"
date: "8/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework#2

For this document I will be embedding the data from the source provided by Professor Rice in Homework#1. I am choosing to work with the SCDB dataset. This dataset stems from a ".csv file provided by Professor Rice in Homework#1. SCDB stands for the Supreme Court Database Code Book. 

```{r}
library(tidyverse)

scdbData <- read.delim("scdb.csv", sep = ",", header= TRUE)

head(scdbData)
```

## Retrieving Basic Information

As stated in the assignment I am aiming to retreive the number of observations in the Dataset as well as the number of variables.
I chose to get the number of observations(rows) by using the "dim" function to get the dimensions of the Dataset. 
To get the number of variables in the Dataset I went ahead and used the same function. Using the "dim" function retrieves both the rows and columns within a Dataset.

```{r}
dim(scdbData)

```

## Explination

Given the retrieved dimensions of 8966 x 53 we can understand that this Dataframe is 8966 rows(observations) by 53 columns(variables). You can also use the functions "nrow" and "ncol" respectively to get individual values
